Legacy Data Confounds Genomics Studies

### 2019-04-30 legacy.tex
added discussion of weird regions

With the exception of chromosome 1 these variants appear to be evenly distributed across chromosomes (Figure \ref{CountPerChrom}).
Clusters of variants reaching significance are apparent in 10kb regions of the genome (Figure \ref{VariantDensity}).
These regions coincide with regions with known sequencing issues like HLA and other immunoglobulin receptor genes.

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/Omni_AF.jpg}
\caption{We found that 613 of the variants we identified as being associated to $Q$ were present on Illumina's Omni 2.5 chip. Variants highly associated to $Q$ tend to have low global allele frequencies.}}
\label{Omni}
\end{figure}

>>>>

$Q$-associated variants are distributed across the genome, with chromosome 1 showing an excess of such variants, and other chromosomes being relatively uniform (Figure \ref{CountPerChrom}).
At a 10kb scale, we also see rather uniform distribution with a small number of regions showing a strong enrichment for such variants (Figure \ref{VariantDensity}). We identify 56 regions of 10kb each that collectively contain 1132 $Q$- associated (less than 5\% of problematic variants). These regions, which include known challenging regions such as HLA and other immunoglobulin receptor genes, are provided in Supplementary file \sgcomment{XX}. Distribution of association statistics in a sample of these regions is provided in Figure \ref{x}.

@@

\begin{figure}[h]
\includegraphics[width=\hsize,keepaspectratio]{./Figures/Omni_AF.jpg}
\caption{We found that 613 of the variants we identified as being associated to $Q$ were present on Illumina's Omni 2.5 chip. Variants highly associated to $Q$ tend to have low global allele frequencies.}
\label{Omni}
\end{figure}
